Theories of deliberated choice

### 2024-01-15 simple.tex
2 sit for cond HAI

  \begin{theorem}
    \label{th:suffIndic}
    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
    Then, there exists a claim that holds and is anonymous and indicative.
  \end{theorem}
  \begin{proof}
    Define $p = P_{i_1}$.
    Consider any claim $C$ such that $C^\text{HA} \wsub C \wsub C^\text{A}$ and $C$ is anonymous.
    % Define the claim $C$ as $\set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$ (or as anything included in it that includes $C^\text{HA}$ and is anonymous).
    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
  \end{proof}
  \begin{corollary}
    \label{th:suffIndicDec}
    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
  \end{corollary}
  \begin{proof}
    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
    Apply \cref{th:suffIndic}.
  \end{proof}

>>>>

  \begin{theorem}
    \label{th:suffIndic}
    The following two conditions on $\allleadsto$ are equivalent:
    \begin{enumerate}
      \item \label{it:condHAI} for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$;
      \item \label{it:HAI} there exists a claim that holds and is anonymous and indicative.
    \end{enumerate}
  \end{theorem}
  \begin{proof}
    For \cref{it:condHAI} $\implies$ \cref{it:HAI},
    define $p = P_{i_1}$.
    Consider any claim $C$ such that $C^\text{HA} \wsub C \wsub C^\text{A}$ and $C$ is anonymous.
    % Define the claim $C$ as $\set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$ (or as anything included in it that includes $C^\text{HA}$ and is anonymous).
    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.

    For \cref{it:HAI} $\implies$ \cref{it:condHAI},
    pick an indicative claim $C$ and consider $i \in I$ and $\theta \in \Theta \cap (\allhists × \set{i} × P) \cap C^\wsub$ such that $\pi(\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C)(i) \ssub P$.
    Define $H = \theta^{-1}(i, P)$.
  \end{proof}
  \begin{corollary}
    \label{th:suffIndicDec}
    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
  \end{corollary}
  \begin{proof}
    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
    Apply \cref{th:suffIndic}.
  \end{proof}

  \begin{remark}
    If there are only two types each with a DJ not empty, then the condition of \cref{it:condHAI} is satisfied. More formally, if ${\allleadsto}(I) = \set{{\ileadsto[i_1]}, {\ileadsto[i_2]}}$ and $\emptyset \notin \pi({\allleadsto})(I)$, then \cref{it:condHAI} is satisfied: define $\ar_1, \ar_2$ as some decisive arguments for $i_1, i_2$, respectively, and define $H = \set{(\ar_1, \ar_2)}$.
  \end{remark}

\begin{remark}
  Given $p \in P$, define $I_p = \set{i \in I \suchthat \pi(i) = p}$.
  If $I \setminus I_p$ all have $\ar$ as a decisive argument, then \cref{it:condHAI} is satisfied: if $I_p \neq \emptyset$, pick $i \in I_p$, let $\ar'$ be a decisive argument for $i$, and define $H = \set{(\ar, \ar')}$; otherwise, define $H = \set{(\ar)}$.
\end{remark}
